\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-13 analytics/usage.tex
Finish 4.1

@@

  \fbox {
    \includegraphics[width=8cm]{images/skedge/blocks}
  }

  \caption{Etc}
  \label{fig:searchtypes}

@@

40\% of sessions have at least one block-click
Average of 5.12 block-clicks per session

success because you can't click schedule blocks in better cdcs!!

>>>>

\subsection{Social}

Since March 1st (40 days), based on 963 sessions on {\tt /social}, Skedge Social has seen\ldots

\vspace{5pt}

\singlespacing
\begin{center}
\begin{tabular}{l}
  \hline
  141 users have linked Skedge to Facebook \\
  10,242 page views (256 page views/day)  \\
  10 pages/session (users cycle through tabs and go back to it) \\
  a 5\% bounce rate (users interact with it) \\
  67\% of visits being were returning visitors \\
  284 overlays onto friends’ schedules (2 per user) \\
  \hline
\end{tabular}
\end{center}
\doublespacing

\vspace{5pt}

\noindent Although the feature is too young for in-depth data analysis, these initial reports show promise, especially in the rate of adoption (around 3.5 users per day on average), its level of interaction, and the rate of \emph{returning} users to Skedge Social.

@@

\begin{figure}
  \centering

  \fbox {
    \includegraphics[width=6cm]{images/skedge/blocks}
  }

  \caption{Hovering over a course block in Skedge's side-schedule shows at-a-glance information about it; clicking on it navigates the user to that course}
  \label{fig:searchtypes}

@@

As a user adds courses to their schedule, the courses appear as timeblocks on the schedule to the side of the search results. The blocks only display the course code (i.e. department code, course number, and if it is a subsection such as a lab or workshop), but hovering over them displays more useful information like the course title, location, and the exact start and end times.

Interestingly, the only course information that is gained by clicking on courses is the description, instructor, and perhaps minor details like course comments, prerequisites, etc. Yet, of 12,944 sessions of users with schedules, \textbf{40\%} of those sessions had at least one block-click. Those sessions with block clicks averaged \textbf{5.12 block-clicks per session}, a strikingly high number considering its limited functional use! How do we explain this?

I hypothesize that a combination of Skedge's presentation of information, its highly interactive user interface, and its concern for quality of user experience contribute to a sense of enjoyment regarding course scheduling. Clicking an average of five times \emph{per session} corresponds to clicking on the blocks for each of his or her courses, glancing over the details, and perhaps reading over the course description. This enamorment with one's course selection is a large component of Skedge's mission. It may seem trivial to state, but I believe the courses one takes in college are paramount to one's personal development and outlook on life. I believe ensuring that students are excited about their course selection and can also freely explore what more knowledge their university has to offer them is key to a well-balanced college experience.

The above could only be confirmed with involved user studies, which I do not have any data for. At the very least, the average block-clicks per session is a strong case for Skedge's usability over CDCS for the simple reason that Better CDCS does not even allow users to click on their schedule blocks, and this usage data shows that there is clearly a desire to do so.
